ext_risk_copula

### 2019-02-20 ext_risk_copula.Rmd
bug fixed
minor changes

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(rlist),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

@@

qrng<-runif(10000,min=0,max=r_bf_pennycuick)
qr<-quantile(qrng,probs=c(.025,.975))

@@

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = c(2,7),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

>>>>

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

@@

qrng<-runif(10000,min=1,max=r_bf_pennycuick) # r must be > 1
qr<-quantile(qrng,probs=c(.025,.975))

@@

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")
